Supplemental Materials, Methods and Results

### 2022-04-14 supp/Supplemental Materials and Methods.Rmd
Added some code that pivots_wide longer to convert wide to long, and hopefully don't lose data anymore.

      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

>>>>

      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################
        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long_t <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% data.frame()
